Implementing Option Pricing Model

### 2019-12-19 draft.Rmd
Reorganizing image files.

![This is the result by comparing Blach-Schoels Merton option price with Monte Carlo methods.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\Result.PNG)

@@

![This is the call payoff from Monte Carlo simulation, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\Naive.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\DeltaHedging.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\DeltaGammaHedging.PNG)

@@

![This is the call payoff from Jump world with Delta-hedging, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma-hedging, used 252 time steps, and 100 simulation.](C:\Users\profile\Desktop\zhaoming\Rmd-Template\Paper\DeltaGammaHedgingJump.PNG)

>>>>

![This is the result by comparing Blach-Schoels Merton option price with Monte Carlo methods.](images/Result.PNG)

@@

![This is the call payoff from Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/Naive.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/DeltaHedging.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/DeltaGammaHedging.PNG)

@@

![This is the call payoff from Jump world with Delta-hedging, used 252 time steps, and 100 simulation.](images/DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma-hedging, used 252 time steps, and 100 simulation.](images/DeltaGammaHedgingJump.PNG)

### 2019-12-19 draft.tex
Reorganizing image files.

\title{Implementing Option Pricing Modle  }

@@

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Zhao Ming (Utah State University)},
             pdfkeywords = {Monte Carlo, control variates, option pricing},  
            pdftitle={Implementing Option Pricing Modle},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/Result.PNG}
\caption{This is the result by comparing Blach-Schoels Merton option
price with Monte Carlo methods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/Naive.PNG}
\caption{This is the call payoff from Monte Carlo simulation, used 252
time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/DeltaHedging.PNG}
\caption{This is the call payoff from Delta-Hedged Monte Carlo
simulation, used 252 time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/DeltaGammaHedging.PNG}
\caption{This is the call payoff from Delta-Hedged Monte Carlo
simulation, used 252 time steps, and 100 simulation.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/DeltaHedgingJump.PNG}
\caption{This is the call payoff from Jump world with Delta-hedging,
used 252 time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/profile/Desktop/zhaoming/Rmd-Template/Paper/DeltaGammaHedgingJump.PNG}
\caption{This is the call payoff from Jump world with
Delta-Gamma-hedging, used 252 time steps, and 100 simulation.}
\end{figure}

>>>>

\title{Implementing Option Pricing Model  }

@@

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Zhao Ming (Utah State University)},
             pdfkeywords = {Monte Carlo, control variates, option pricing},  
            pdftitle={Implementing Option Pricing Model},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{figure}
\centering
\includegraphics{images/Result.PNG}
\caption{This is the result by comparing Blach-Schoels Merton option
price with Monte Carlo methods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/Naive.PNG}
\caption{This is the call payoff from Monte Carlo simulation, used 252
time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/DeltaHedging.PNG}
\caption{This is the call payoff from Delta-Hedged Monte Carlo
simulation, used 252 time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/DeltaGammaHedging.PNG}
\caption{This is the call payoff from Delta-Hedged Monte Carlo
simulation, used 252 time steps, and 100 simulation.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/DeltaHedgingJump.PNG}
\caption{This is the call payoff from Jump world with Delta-hedging,
used 252 time steps, and 100 simulation.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/DeltaGammaHedgingJump.PNG}
\caption{This is the call payoff from Jump world with
Delta-Gamma-hedging, used 252 time steps, and 100 simulation.}
\end{figure}
